Analysis of the properties of probabilistic models in learning problems with an expert\thanks{Grants or other notes about the article that should go on the front page should be placed here. General acknowledgments should be placed at the end of the article.}

### 2020-12-30 paper/Bazarova2020Springer/article.tex
add all

%\titlerunning{Short form of title}        % if too long for running head

@@

\section{Introduction}
\label{intro}
Interpretable model building in machine learning~\cite{Ribeiro2016} is one of the key challenges.
Modern solutions of the image classification problem based on deep learning networks ResNet, VGG, Intercept~\cite{Kaiming2015} are poorly interpreted models.
The papers~\cite{Han2020} \cite{Xingjun2019} \cite{Akhtar2018} show that deep learning networks are sensitive even to small noise in the data, which is due to their uninterpretability.

@@

% Non-BibTeX users please use
\begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
\bibitem{Ribeiro2016}
Marco Tulio Ribeiro, Sameer Singh, Carlos Guestrin, Why Should I Trust You?": Explaining the Predictions of Any Classifier, Proceedings of the 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining, 1135--1144 (2016)

\bibitem{Tianqi2016}
Chen Tianqi, Guestrin Carlos, XGBoost: A Scalable Tree Boosting System, KDD ’16 Proceedings of the 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining (2016)

\bibitem{Ishwaran2012}
Chen Xi, Ishwaran Hemant, Random Forests for Genomic Data Analysis, Genomics, Vol. 6, 323--329 (2012)

\bibitem{Yuksel2012}
Yuksel Seniha Esen, Wilson Joseph N., Gader Paul D, Twenty Years of Mixture of Experts, IEEE Transactions on Neural Networks and Learning Systems, Vol. 8, 1177--1193 (2012)

\bibitem{Cao2003}
L.~Cao, Support vector machines experts for time series forecasting, Neurocomputing, Vol. 51, 321--339 (2003)

\bibitem{Dempster1977}
A. P. Dempster, N. M. Laird and D. B. Rubin, Maximum Likelihood from Incomplete Data via the EM Algorithm, Journal of the Royal Statistical Society. Series B (Methodological), Vol. 39, 1--38 (1997)

\bibitem{Yumlu2003}
M.\,S.~Yumlu, F.\,S.~Gurgen,  N.~Okay, Financial time series prediction using mixture of experts, In Proc. 18th Int. Symp. Comput. Inf. Sci., 553--560 (2003)

\bibitem{Cheung1995}
Y.~M.~Cheung, W.~M.~Leung, and L. Xu,  Application of mixture of experts model to financial time series forecasting, In Proc. Int. Conf. Neural Netw. Signal Process., 1--4 (1995)

\bibitem{Weigend2000}
A. S. Weigend, S. Shi, Predicting daily probability distributions of S\&P500 returns, J. Forecast., Vol. 19, 375--392 (2000)

\bibitem{Ebrahimpour2009}
A.~Estabrooks, N.~Japkowicz, Recognition of Persian handwritten digits using characterization loci and mixture of experts, J. Digital Content Technol. Appl., 42--46 (2009)

\bibitem{Estabrooks2001}
R. Ebrahimpour, M. R. Moradian, A. Esmkhani, F. M. Jafarlou, A mixture-of-experts framework for text classification, In Proc. Workshop Comput. Natural Lang. Learn., Assoc. Comput. Linguist., 1--8 (2009)

\bibitem{Mossavat2010}
S. Mossavat, O. Amft, B. de Vries, P. Petkov, W. Kleijn, A Bayesian hierarchical mixture of experts approach to estimate speech quality, In Proc. 2nd Int. Workshop Qual. Multimedia Exper., 200--205 (2010)

\bibitem{Sminchisescu2007}
C. Sminchisescu, A. Kanaujia, and D. Metaxas, B M3 E: Discrimina- tive density propagation for visual tracking, IEEE Trans. Pattern Anal. Mach. Intell., Vol. 29, 2030--2044 (2007)

\bibitem{Matveev2010}
I. Matveev, Detection of iris in image by interrelated maxima of brightness gradient projections, Appl.Comput. Math, Vol. 9, 252--257 (2010)

\bibitem{Matveev2014}
I. Matveev, I. Simonenko, Detecting precise iris boundaries by circular shortest path method, Pattern Recognition and Image Analysis, Vol. 24, 304--309 (2014)

\bibitem{Bowyer2010}
K. Bowyer, K. Hollingsworth, P. Flynn, A Survey of Iris Biometrics Research (2010)

\bibitem{Peng1996}
F. Peng, R. A. Jacobs, M. A. Tanner, Bayesian inference in mixtures-of-experts and hierarchical mixtures-of-experts models with an application to speech recognition, J. Amer. Stat. Assoc., Vol. 91, 953--960 (1996)

\bibitem{Tuerk2001}
A. Tuerk,  The state based mixture of experts HMM with applications to the recognition of spontaneous speech, Ph.D. thesis, Dept. Eng., Univ. Cambridge, Cambridge, U.K. (2001)

\bibitem{bishop2006}
Bishop C., Pattern Recognition and Machine Learning, 758, Springer, Berlin (2010)

\bibitem{Kaiming2015}
Kaiming He, Deep Residual Learning for Image Recognition (2015)

\bibitem{Han2020}
Han Xu, Adversarial Attacks and Defenses in Images, Graphs and Text: A Review (2020)

\bibitem{Xingjun2019}
Xingjun Ma, Understanding Adversarial Attacks on Deep Learning Based Medical Image Analysis Systems (2019)

\bibitem{Akhtar2018}
Naveed Akhtar, Threat of Adversarial Attacks on Deep Learning in Computer Vision: A Survey (2018)

\bibitem{Dalila2018}
Salamani Dalila, Deep generative models for fast shower simulation in ATLAS (2018)

>>>>

\titlerunning{Probabilistic models in learning with an expert}        % if too long for running head

@@

\section{Introduction}
\label{intro}
Interpretable model building in machine learning~\cite{Ribeiro2016} is one of the key challenges.
Modern solutions of the image classification problem based on deep learning networks ResNet, VGG, Intercept~\cite{Kaiming2015} are poorly interpreted models.
The papers~\cite{Han2020} \cite{Akhtar2018} show that deep learning networks are sensitive even to small noise in the data, which is due to their uninterpretability.

@@

% Non-BibTeX users please use
\begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
\bibitem{Ribeiro2016}
Ribeiro M, Singh S, Guestrin C (2016) Why Should I Trust You?": Explaining the Predictions of Any Classifier. KDD ’16 Proceedings of the 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining 1135--1144

\bibitem{Tianqi2016}
Chen T, Guestrin C (2016) XGBoost: A Scalable Tree Boosting System. KDD ’16 Proceedings of the 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining 785--794

\bibitem{Ishwaran2012}
Chen Xi, Ishwaran H (2012) Random Forests for Genomic Data Analysis. Genomics 6:323--329

\bibitem{Yuksel2012}
Yuksel S, Wilson J, Gader P (2012) Twenty Years of Mixture of Experts. IEEE Transactions on Neural Networks and Learning Systems 8:1177--1193

\bibitem{Cao2003}
Cao L (2003) Support vector machines experts for time series forecasting. Neurocomputing 51:321--339

\bibitem{Dempster1977}
Dempster A, Laird N, Rubin D (1997) Maximum Likelihood from Incomplete Data via the EM Algorithm. Journal of the Royal Statistical Society. Series B (Methodological) 39:1--38

\bibitem{Yumlu2003}
Yumlu M, Gurgen F,  Okay N (2003) Financial time series prediction using mixture of experts. In Proc. 18th Int. Symp. Comput. Inf. Sci. 553--560

\bibitem{Cheung1995}
Cheung Y, Leung W, Xu L (1995) Application of mixture of experts model to financial time series forecasting. In Proc. Int. Conf. Neural Netw. Signal Process. 1--4

\bibitem{Weigend2000}
Weigend A, Shi S (2000) Predicting daily probability distributions of S\&P500 returns. J. Forecast 19:375--392

\bibitem{Ebrahimpour2009}
Estabrooks A, Japkowicz N (2009) Recognition of Persian handwritten digits using characterization loci and mixture of experts. J. Digital Content Technol. Appl. 42--46

\bibitem{Estabrooks2001}
Ebrahimpour R, M. Moradian R, Esmkhani A, Jafarlou F (2009) A mixture-of-experts framework for text classification. In Proc. Workshop Comput. Natural Lang. Learn., Assoc. Comput. Linguist. 1--8

\bibitem{Mossavat2010}
Mossavat S, Amft O, Vries B, Petkov P, Kleijn W (2010) A Bayesian hierarchical mixture of experts approach to estimate speech quality. In Proc. 2nd Int. Workshop Qual. Multimedia Exper. 200--205

\bibitem{Sminchisescu2007}
Sminchisescu C, Kanaujia A, Metaxas D (2007) Discriminative density propagation for visual tracking. IEEE Trans. Pattern Anal. Mach. Intell. 29:2030--2044

\bibitem{Matveev2010}
Matveev I (2010) Detection of iris in image by interrelated maxima of brightness gradient projections. Appl. Comput. Math 9:252--257

\bibitem{Matveev2014}
Matveev I, Simonenko I (2014) Detecting precise iris boundaries by circular shortest path method. Pattern Recognition and Image Analysis 24:304--309

\bibitem{Bowyer2010}
Bowyer K, Hollingsworth K, Flynn P (2010) A Survey of Iris Biometrics Research: 2008-2010. Handbook of iris recognition 15--54

\bibitem{Peng1996}
Peng F, Jacobs R, Tanner M (1996) Bayesian inference in mixtures-of-experts and hierarchical mixtures-of-experts models with an application to speech recognition. J. Amer. Stat. Assoc. 91:953--960

\bibitem{Tuerk2001}
Tuerk A (2001) The state based mixture of experts HMM with applications to the recognition of spontaneous speech. Ph.D. thesis, University of Cambridge.

\bibitem{bishop2006}
Bishop C. (2010) Pattern Recognition and Machine Learning. Springer, Berlin

\bibitem{Kaiming2015}
Kaiming H, Xiangyu Z, Shaoqing R, Jian S (2016) Deep Residual Learning for Image Recognition. Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition 770--778

\bibitem{Han2020}
Han X, Yao M, Debayan D, Hui L, Ji-Liang T, Anil J (2020) Adversarial Attacks and Defenses in Images, Graphs and Text: A Review. International Journal of Automation and Computing 17:151--178

\bibitem{Akhtar2018}
Akhtar N, Mian A (2018) Threat of Adversarial Attacks on Deep Learning in Computer Vision: A Survey. IEEE Access 6:14410--14430

\bibitem{Dalila2018}
Salamani D, Gadatsch S, Golling T,  Stewart G, Ghosh A,  Rousseau D,  Hasib A,  Schaarschmidt J (2018) Deep Generative Models for Fast Shower Simulation in ATLAS. 2018 IEEE 14th International Conference on e-Science (e-Science) \text{https://doi.org/10.1109/eScience.2018.00091}
